Hydra Battles and Cie

### 2021-09-12 doc/chapter-powers.tex
more snippets

\begin{Coqsrc}
Section M_given.
 Variables (A:Type) (E_op : Mult_op A)(E_one:A) (E_eq : Equiv A).
 Context (M:EMonoid  E_op E_one E_eq).
\end{Coqsrc}

@@

\begin{Coqsrc}
Ltac monoid_rw :=
    rewrite Eone_left  ||
    rewrite Eone_right  || 
    rewrite Eop_assoc .

Ltac monoid_simpl := repeat monoid_rw.

Section About_power.
\end{Coqsrc}

In order to make possible proof by rewriting on expressions which contain
the exponentiation operator, we have to prove that, whenever \texttt{$x$ == $y$},
the equality \texttt{$x^n$ == $y^n$} holds for any exponent \texttt{$n$}. 
For this purpose, we use the \texttt{Proper} class of module
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Classes.Morphisms.html}{Coq.Classes.Morphisms}
\index{coq}{Type classes}
\index{coq}{Type classes!Proper class}
\begin{Coqsrc}
Global Instance power_proper :
     Proper (equiv ==> eq ==> equiv) power.
(* Proof omitted *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma power_of_plus :   forall x n p, x ^ (n + p) ==  x ^ n *  x ^ p.
(* Proof omitted *)

Ltac power_simpl := 
    repeat (monoid_rw || rewrite <- power_x_plus).
\end{Coqsrc}

>>>>

\inputsnippets{Pow/MGiven}

@@

\inputsnippets{Pow/MonoidRw}

In order to make possible proof by rewriting on expressions which contain
the exponentiation operator, we have to prove that, whenever \texttt{$x$ == $y$},
the equality \texttt{$x^n$ == $y^n$} holds for any exponent \texttt{$n$}. 
For this purpose, we use the \texttt{Proper} class of module
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Classes.Morphisms.html}{Coq.Classes.Morphisms}
\index{coq}{Type classes}
\index{coq}{Type classes!Proper class}

\inputsnippets{Pow/powerProper}

@@

\inputsnippets{Pow/powerOfPlus, Pow/powerSimpl}
